The MRChem MRA code for molecular electronic calculations. Performance and scaling properties

### 2022-02-17 main.tex
test
Updates from Overleaf

@@

Figure \ref{fig01} show computation times divided by the number of orbitals for alkanes of different lengths. For a linear scaling method, the time per orbital should approximately constant. The time per orbital less than doubles going from the smallest (81 orbitals) to the largest (1121 orbitals) alkane, i.e close to linear scaling. % quadratic scaling would multiply the time by 13.8

@@

The number of non-negligible exchange contributions should ideally grow linearly with system size for large enough systems, and therefore the exchange computation time per orbital should be constant. However exchange contributions are the result of the sum of terms, and if the number of terms increase the accuracy of each individual term must be increased in order to achieve a fixed absolute precision in the final result. In our implementation, we scale the required precision of the individual terms by a factor proportional to the square root of the number of orbitals.

Note that the definition of what one means by "linear scaling" is not the same in this paper and in the field of traditional Gaussian set. In the latter one usually mean a fixed sized basis set for a subsystem, and then the number (N) of subsystems is growing. If the runtime is increasing linearly with the number of subsystems, one usually assume that linear scaling is achieved. In this paper the runtime for a fixed absolute precision is studied for different sizes. Since a fixed error $\epsilon$ per subsystem will lead to a total error on the system which grows as $\epsilon \sqrt{N} $ with system size, the accuracy per subsystem must then be increased to achieve a fixed absolute error for the entire system. This is the main reason why our runtimes are not ex
\subsection{Scaling with precision}

%Table TO UPDATE!
\begin{table*}[t]
    \centering
    \begin{tabular}{cccccccccc}
& Exchange &  Coulomb & Kinetic energy& Helmholtz & Total \\
 Valinomycine 1E-5& 35.8&6.7 & 1.5 & 1.7 & 51.6\\
Valinomycine 1E-6& 87.6 &17.2 & 3.0& 4.2 &127.8\\
Valinomycine 1E-7& 211.2& 50.9& 6.1&12.7& 322.3 \\
Valinomycine 1E-8  & 531.0& 163.9& 12.9&32.7& 852.6 \\
 Gramicidin 1E-5&3.3& 0.3 & 0.1& 0.2&4.31 \\
  Gramicidin 1E-6& 9.1& 0.5& 0.2& 0.4&11.4\\
  Gramicidin 1E-7& 24.6&3.1& 0.6& 2.2&  35.7\\
    \end{tabular}
    \caption{Time for different terms in the SCF cycle (val seconds 4864 cores, gram 4284 cores minutes)}
    \label{tab:times}
\end{table*}

>>>>

Only a superficial overview of the method is given here, as more detailed descriptions can be found elsewhere REF.

@@

Figure \ref{fig01} show computation times divided by the number of orbitals for alkanes of different lengths. For a linear scaling method, the time per orbital should be approximately constant.  The time per orbital less than doubles going from the smallest (81 orbitals) to the largest (1121 orbitals) alkane, i.e close to linear scaling. 
% quadratic scaling would multiply the time by 13.8

@@

The number of non-negligible exchange contributions should ideally grow linearly with system size for large enough systems, and therefore the exchange computation time per orbital should be constant. However exchange contributions are the result a the sum of terms, and if the number of terms increase the accuracy of each individual term must be increased in order to achieve a fixed absolute precision in the final result. In our implementation, this is taking care of by increasing the required precision of the individual terms by a factor proportional to the square root of the number of orbitals. This is the main reason why our run times are not exhibiting a clearer linear trend.

%Note that the definition of what one means by "linear scaling" is not the same in this paper and in the field of traditional Gaussian set. In the latter one usually mean a fixed sized basis set for a subsystem, and then the number (N) of subsystems is growing. If the runtime is increasing linearly with the number of subsystems, one usually assume that linear scaling is achieved. In this paper the runtime for a fixed absolute precision is studied for different sizes. Since a fixed error $\epsilon$ per subsystem will lead to a total error on the system which grows as $\epsilon \sqrt{N} $ with system size, the accuracy per subsystem must then be increased to achieve a fixed absolute error for the entire system. This is the main reason why our runtimes are not ex
\subsection{Scaling with precision}

%Table TO UPDATE!
\begin{table*}[t]
    \centering
    \begin{tabular}{cccccccccc}
& Exchange &  Coulomb & Kinetic energy& Helmholtz & Total \\
 Valinomycine 1E-5& 35.8&6.7 & 1.5 & 1.7 & 51.6\\
Valinomycine 1E-6& 87.6 &17.2 & 3.0& 4.2 &127.8\\
Valinomycine 1E-7& 211.2& 50.9& 6.1&12.7& 322.3 \\
Valinomycine 1E-8  & 531.0& 163.9& 12.9&32.7& 852.6 \\
 Gramicidin 1E-5&3.3& 0.3 & 0.1& 0.2&4.31 \\
  Gramicidin 1E-6& 9.1& 0.5& 0.2& 0.4&11.4\\
  Gramicidin 1E-7& 24.6&3.1& 0.6& 2.2&  35.7\\
    \end{tabular}
    \caption{Time for different terms in the SCF cycle (val seconds 16 nodes, gram 4284 cores minutes)}
    \label{tab:times}
\end{table*}
